---
title: "Introduction to geouy"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Installation

**geouy** is an R package that allows users to easily access official spatial data sets of Uruguay. The package includes a wide range of geospatial datasets as *simple features* (`sf`), available at various geographic scales and for various years with harmonized attributes and projection (see detailed list below).

```r
# From CRAN
  install.packages("geouy")
  library(geouy)
  
# Use the development version with latest features
  utils::remove.packages('geouy')
  devtools::install_github("RichDeto/geouy")
  library(geouy)
```

obs. If you use **Linux**, you need to install a couple dependencies before installing the libraries `sf` and `geouy`. [More info here](https://github.com/r-spatial/sf#linux).


## load_geouy()

The syntax of all `geouy` functions operate one the same logic so it becomes intuitive to download any data set using a single line of code. Like this:

```R
secc <- load_geouy("Secciones")
```

### Exercise 

Please write the code to obtain the geometries of "Peajes" in a object `peaje`

```{r load, exercise=TRUE, exercise.lines = 5}

```

## where_uy() 

You get an `sf` object of one or more administrative units in Uruguay, according to a query by code or name in the layer.

Please write the code to obtain the geometries of "Peajes" in a object `peaje`

```{r where, exercise=TRUE, exercise.lines = 5}

```

## add_geom()

This function allows you to add a `geom` variable with a code variable of "zona", "barrio", "localidad", "segmentos", "secciones" or "departamentos".

## geocode_ide_uy() 

Allows geocoding directions using IDE_uy.

## plot_geouy()

Plot a variable of your `sf` object with north and scale, set on a simple theme.

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

## Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
